---
title: "tfserve: Tensorflow Serve Examples"
output:
  github_document:
    fig_width: 9
    fig_height: 5
    toc: true
    toc_depth: 3
---


```{r setup, include=FALSE}
library(tensorflow)
knitr::opts_chunk$set(eval = TRUE)
```

## Overview

This repo provides tools and examples to serve Tensorflow models from R. The process has two stages:

- Save the model
- Deploy (serve) the model

The way the model is saved varies based on the package that was used to create it.  

## Saving a Tensorflow model

One can train MNIST as described by [MNIST For ML Beginners](https://tensorflow.rstudio.com/tensorflow/articles/tutorial_mnist_beginners.html) and track
the model's inputs and outputs named `x` and `y` under that particular article. For convinience, we can
run instead:

```{r}
library(tensorflow)
library(tfserve)

sess <- tf$Session()
mnist_model <- tfserve_mnist_train(sess)
```

Once trained, the model can be saved with [SavedModelBuilder](https://www.tensorflow.org/api_docs/python/tf/saved_model/builder/SavedModelBuilder).

```{r}
if (dir.exists("trained")) unlink("trained", recursive = TRUE)

model_path <- file.path("trained/tensorflow-mnist/1")

builder <- tf$saved_model$builder$SavedModelBuilder(model_path)
builder$save()

dir(model_path, recursive = TRUE)
```

However, saving the model is not sufficient when using Tensorflow Serving, see [Serving a Tensorflow Model](https://www.tensorflow.org/serving/serving_basic).

Instead, we need to create a signature for the model, which will require references to the
input and output Tensors for the model which we retrieved from the model:

```{r}
mnist_model
```

with them, we can use the following convenience function to retrieve the signature for the model:

```{r}
signature <- tfserve_mnist_signature(mnist_model$input, mnist_model$output)
```

This signature can be used in combination with `SavedModelBuilder.add_meta_graph_and_variables` to
provide a model usable with Tensorflow Serving:

```{r}
tfserve_save(sess, model_path, signature, overwrite = TRUE)

dir(model_path, recursive = TRUE)
```

## Saving a TFEstimators model

A sample model using the `mtcars` data frame is trained using `tfestimators`.  The resulting model is the one that will be saved to disk. To train, we can follow the TensorFlow estimators [Quick Start](https://tensorflow.rstudio.com/tfestimators/); or for convenienve, run:

```{r}
library(tfestimators)

model <- tfserve_mtcars_train()
```

The `export_savemodel()` will create the **pb** file and the **variables** folder

```{r}
#Create an input spec
input_spec <- regressor_parse_example_spec(feature_columns = feature_columns( 
                                             column_numeric("disp", "cyl")
                                           ),
                                           label_key = "input",
                                           label_dtype = tf$string)

# Parse the spec as an input receiver 
input_receiver <- tf$estimator$export$build_parsing_serving_input_receiver_fn(input_spec)

export_savedmodel(model, 
                  export_dir_base = "trained/tfestimators-mtcars",
                  serving_input_receiver_fn = input_receiver)

model_folder <- list.files()[1]
dir(model_path, recursive = TRUE)
```

## Saving a Keras Model

First train a `keras` model as described under [R interface to Keras](https://tensorflow.rstudio.com/keras/), for convinience, run instead:

```{r}
library(keras)
model <- tfserve_mnist_keras_train(epochs = 1)
```

Then use the TensorFlow backend to export the model (see also [/keras/issues/6212](https://github.com/fchollet/keras/issues/6212) and [Exporting a model with TF Serving from Keras blog](https://blog.keras.io/keras-as-a-simplified-interface-to-tensorflow-tutorial.html#exporting-a-model-with-tensorflow-serving)):

```{r}
model_path <- "trained/keras-mnist/1"

sess <- backend()$get_session()

signature <- tfserve_mnist_signature(
  model$input_layers[[1]]$input,
  model$output_layers[[1]]$output)

tfserve_save(sess, model_path, signature, overwrite = TRUE)

dir(model_path, recursive = TRUE)
```

## Serving Models

See [Tensorflow Serving Setup](https://www.tensorflow.org/serving/setup#installing_using_apt-get), but in general, from Linux, first install prereqs:

```{bash eval=F}
sudo apt-get update && sudo apt-get install -y build-essential curl libcurl3-dev git libfreetype6-dev libpng12-dev libzmq3-dev pkg-config python-dev python-numpy python-pip software-properties-common swig zip zlib1g-dev
```

Then install Tensorflow Serving:

```{bash eval=F}
echo "deb [arch=amd64] http://storage.googleapis.com/tensorflow-serving-apt stable tensorflow-model-server tensorflow-model-server-universal" | sudo tee /etc/apt/sources.list.d/tensorflow-serving.list

curl https://storage.googleapis.com/tensorflow-serving-apt/tensorflow-serving.release.pub.gpg | sudo apt-key add -

sudo apt-get update && sudo apt-get install tensorflow-model-server
```

Optionally, install the api client:

```{bash eval=F}
sudo pip install tensorflow-serving-api --no-cache-dir
```

Then serve the TensorFlow model using:

```{bash eval=F}
tensorflow_model_server --port=9000 --model_name=mnist --model_base_path=/mnt/hgfs/tfserve/trained/tensorflow-mnist
```

```
2017-10-04 14:53:15.291409: I external/org_tensorflow/tensorflow/cc/saved_model/loader.cc:284] Loading SavedModel: success. Took 113175 microseconds.
2017-10-04 14:53:15.293200: I tensorflow_serving/core/loader_harness.cc:86] Successfully loaded servable version {name: mnist version: 1}
2017-10-04 14:53:15.299338: I tensorflow_serving/model_servers/main.cc:288] Running ModelServer at 0.0.0.0:9000 ...
```

Or the `tfestimators` model using:

```{bash eval=F}
tensorflow_model_server --port=9000 --model_name=mnist --model_base_path=/mnt/hgfs/tfserve/trained/tfestimators-mtcars
```

```
2017-10-04 15:33:21.279211: I external/org_tensorflow/tensorflow/cc/saved_model/loader.cc:284] Loading SavedModel: success. Took 43820 microseconds.
2017-10-04 15:33:21.281129: I tensorflow_serving/core/loader_harness.cc:86] Successfully loaded servable version {name: mnist version: 1507156394}
2017-10-04 15:33:21.284161: I tensorflow_serving/model_servers/main.cc:288] Running ModelServer at 0.0.0.0:9000 ...

```

One can use `saved_model_cli` to inspect model contents, as in:

```{bash eval=F}
saved_model_cli show --dir /mnt/hgfs/tfserve/trained/tensorflow-mnist/1
```

## Using Models

Manually download [mnist_client.py](https://raw.githubusercontent.com/tensorflow/serving/master/tensorflow_serving/example/mnist_client.py) and [mnist_input_data.py](https://raw.githubusercontent.com/tensorflow/serving/master/tensorflow_serving/example/mnist_input_data.py). Then run:

```{bash eval=F}
python mnist_client.py --num_tests=1000 --server=localhost:9000

Successfully downloaded train-images-idx3-ubyte.gz 9912422 bytes.
Extracting /tmp/train-images-idx3-ubyte.gz
Successfully downloaded train-labels-idx1-ubyte.gz 28881 bytes.
Extracting /tmp/train-labels-idx1-ubyte.gz
Successfully downloaded t10k-images-idx3-ubyte.gz 1648877 bytes.
Extracting /tmp/t10k-images-idx3-ubyte.gz
Successfully downloaded t10k-labels-idx1-ubyte.gz 4542 bytes.
Extracting /tmp/t10k-labels-idx1-ubyte.gz
........................................
Inference error rate: 9.5%
```
