---
title: "Exporting Models"
---

```{r setup, include=FALSE}
library(tensorflow)
knitr::opts_chunk$set(eval = TRUE)
```

The first step towards deploying a trained model is to export this model from
TensorFlow. This guide demostrates how to export SavedModels from: TensorFlow,
tfestimators and keras using `export_savedmodel()`

## Exporting from TensorFlow

Exporting a SavedModel from TensorFlow requires input and output tensors to be
passed to `export_savedmodel()`.

For instance, one can train MNIST as described by [MNIST For ML Beginners](https://tensorflow.rstudio.com/tensorflow/articles/tutorial_mnist_beginners.html), track
the model's inputs and outputs named `x` and `y` under that particular article and
call `export_savedmodel()` as follows:

```{r eval=F}
export_savedmodel(sess, "tensorflow-mnist", inputs = list(images = x), outputs = list(scores = y))
```

For convinience, a sample training script is included in `tfdeploy` to train and
export this MNIST model as follows:

```{r}
tfruns::training_run(system.file("models/tensorflow-mnist.R", package = "tfdeploy"))
dir("tensorflow-mnist", recursive = TRUE)
```

## Exporting from TFEstimators

A sample model using the `mtcars` data frame is trained using `tfestimators`.  The resulting model is the one that will be saved to disk. To train, we can follow the TensorFlow estimators [Quick Start](https://tensorflow.rstudio.com/tfestimators/); or for convenienve, run:

```{r eval=F}
library(tfestimators)

mtcars_train <- function () {
  mtcars_input_fn <- function(data) {
    input_fn(data,
             features = c("disp", "cyl"),
             response = "mpg")
  }

  cols <- feature_columns(
    column_numeric("disp"),
    column_numeric("cyl")
  )

  model <- linear_regressor(feature_columns = cols)

  indices <- sample(1:nrow(mtcars), size = 0.80 * nrow(mtcars))
  train <- mtcars[indices, ]
  test  <- mtcars[-indices, ]

  model %>% train(mtcars_input_fn(train))

  model
}

model <- mtcars_train()
```

The `export_savemodel()` will create the **pb** file and the **variables** folder

```{r eval=F}
# Create an input spec
input_spec <- regressor_parse_example_spec(feature_columns = feature_columns( 
                                             column_numeric("disp", "cyl")
                                           ),
                                           label_key = "input",
                                           label_dtype = tf$string)

# Parse the spec as an input receiver 
input_receiver <- tf$estimator$export$build_parsing_serving_input_receiver_fn(input_spec)

export_savedmodel(model, 
                  export_dir_base = "trained/tfestimators-mtcars",
                  serving_input_receiver_fn = input_receiver)

model_folder <- list.files()[1]

dir(model_path, recursive = TRUE)
```

## Exporting from Keras

First train a `keras` model as described under [R interface to Keras](https://tensorflow.rstudio.com/keras/), for convinience, run instead:

> Notice `set_learning_phase(TRUE)` to prevent 'You must feed a value for
> placeholder tensor 'dropout_1/keras_learning_phase' while serving set learning
> phase (see [stackoverflow.com/q/42025660](https://stackoverflow.com/questions/42025660/keras-set-learning-phase-for-dropout-when-saving-tensorflow-session),
> [keras/issues/2310](https://github.com/fchollet/keras/issues/2310), 
> [keras/issues/7720](https://github.com/fchollet/keras/issues/7720),
> [/tensorflow/serving/issues/310](https://github.com/tensorflow/serving/issues/310)).

```{r eval=F}
library(keras)
tf$reset_default_graph()

backend()$set_learning_phase(TRUE)

model <- mnist_train_keras(epochs = 1)
```

Then save using `export_savedmodel()` as follows:

```{r eval=F}
export_savedmodel(model, "trained/keras-mnist/1")

dir(model_path, recursive = TRUE)
```
